---
title: "CV"
author: "Author"
output: 
  pdf_document:
    latex_engine: pdflatex
    template: template.tex
    keep_tex: true
fontawesome: yes
email: email
github: github
institution: "Institution"
instadd: "institution address"
phone: "phone number"
---
<!-- NOTE: Commands -->

<!-- \sh : subheading -->
<!-- \ssh : subsubheading -->
<!-- \ri : item -->
<!-- \rsi : subitem -->

```{r setup, include=F}
library(tidyverse)
source("cv_functions.R")
ref <- read_tsv("references.csv")
dt <- read_tsv("entries.csv")
knitr::opts_chunk$set(echo=F,warning=F,message=F,results = "asis")
```

# Research interests

Your research interests

# References

```{r ref}
ref %>%
  print_ref() %>% cat()
```

# Graduate Studies

```{r}
print_entries(dt,"graduate","item") %>% cat()
```

# Undergraduate Studies

```{r}
print_entries(dt,"undergraduate","item") %>% cat()
```

# Teaching Experience

```{r}
print_entries(dt,"teaching","text") %>% cat()
```

# Work Experience

```{r}
print_entries(dt,"work","text") %>% cat()
```


# Languages and technical skills

- __Languages__: Italian (native), English (Full proficiency), Spanish (basic) 

- __Software__: MS Office, \LaTeX, Bloomberg, Datastream 

- __Programming__: _Advanced_ : R, RStudio, Stata, Julia, Python, Matlab; _Intermediate_: SQL


# Conferences and seminars

```{r}
print_entries(dt,"conferences","text") %>% cat()
```


# Grants and awards

```{r}
print_entries(dt,"grants","text") %>% cat()
```


# Ongoing projects

```{r}
print_entries(dt,"research","text") %>%  cat()
```
